Title

### 2024-06-09 paper/main.tex
Updates

\subsection{Conditional Case}

\subsection{Connection to special cases}

\section{Web Tool}
As most of the DAGs in practice are built manually, we use our mixed data effect size measure to build a web-tool that aids researches in building DAGs.

>>>>

\subsection{Conditional Case}
For the conditional case we use an approach similar to partial correlation. We
combine the mixed data residualization approach proposed in Ankan 2023. We then
use a canonical correlation based measure on these residuals to get an effect
size.

\subsection{Connection to special cases}
This natually is a generalization of partial correlations. Furthermore, it is 
also a generalization of discrete case.

\section{Using measure of association for modifying DAGs}
The idea behind using the measure of association for modifying DAGs is that,
for any given model and a dataset, we can use the condtiional measure of
association to compute the amount of correlation in the data that is still not
explained by the model. Based on this, we can compute how much improvement in
the explanation would happen if we were to add an edge between variables. This
can then be ranked using the maximum improvement.

Theorem - If we have access to an oracle that can give all correct results, 
the algorithm above is consistent.

\section{Web Tool}
Based on the approach outlined in the previous section, we built a web-based
tool that researchers can upload their dataset to and apply this method to
interactively draw models.

\todo[inline]{List some of the features of the online platform}
